---
title: "Results_prediction_V3"
author: "Anaïs Marquisseau"
date: "15/06/2022"
output: 
  html_document :
    toc: true
    toc_depth: 4
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Libraries

```{r libraries, message=FALSE, warning=FALSE}
rm(list = ls(all.names = TRUE))
gc()

library(tidyverse)
library(knitr)
library(rsample)
library(plotly)
library(ggpubr)
library(multcompView)

theme_set(theme_minimal())

source("t_tests.R")
```

```{r data, message=FALSE, warning=FALSE}
df_SC_V3 = read_tsv("for_cluster/V3/df_SC_V3")

set.seed(53)
cv = rsample::vfold_cv(df_SC_V3, repeats = 50, v = 5, strata = annee_lignee)

nech = function(object) {
  test = nrow(rsample::testing(object))
  train = nrow(rsample::training(object))
  
  df = data.frame("train" = train, "test" = test)
  
  return(df)
}

nech_sum = purrr::map_dfr(cv$splits, nech) %>%
  summarise_all(sum)

```

Pics Florian
```{r pics metabolites, message=FALSE, warning=FALSE}
metabolites = read_tsv("Data/Metabolites_pics_florian.tsv")

metabolites %>%
  filter(metabolite %in% c("Citrate", "L-Threonine", "B-HydroxyisovalericAcid", "MalicAcid","L-Leucine", "L-Serine")) %>%
  select(ppm)%>%
  as_vector()

best_flo_names = c("L-Leu","L-Leu","L-Leu", 
                   "L-Thr","L-Thr","L-Thr",
                   "L-Ser","L-Ser",
                   "Mal", "Mal","Mal",
                   "B-Hyd","B-Hyd",
                   "Cit")

best_flo_pics = c(0.9660, 1.7200, 3.7400,
                  1.3375, 3.6000, 4.2600,
                  3.8540, 3.9800,
                  2.3760, 2.6750, 4.3000, 
                  1.2720, 2.3680, 
                  2.6000)
```
***

## Predictions {.tabset}


### I. Prediction de l'ingestion {.tabset}

```{r data ingestion, message=FALSE, warning=FALSE}
#Zootechnie
loadings_ingestion_zootech = read_tsv("for_cluster/output_V3/model250/ingestion/loadings_ingestion_zootech_SC_V3.tsv")
metrics_ingestion_zootech =read_tsv("for_cluster/output_V3/model250/ingestion/metrics_ingestion_zootech_SC_V3.tsv")
  
#Buckets
loadings_ingestion_buckets = read_tsv("for_cluster/output_V3/model250/ingestion/loadings_ingestion_buckets_SC_V3.tsv")
metrics_ingestion_buckets = read_tsv("for_cluster/output_V3/model250/ingestion/metrics_ingestion_buckets_SC_V3.tsv")

#All
loadings_ingestion_all = read_tsv("for_cluster/output_V3/model250/ingestion/loadings_ingestion_all_SC_V3.tsv")
metrics_ingestion_all = read_tsv("for_cluster/output_V3/model250/ingestion/metrics_ingestion_all_SC_V3.tsv")
```
***

#### 1. Zootechnie + Fixes

##### a) metrics
```{r metriques ZI, message=FALSE, warning=FALSE}
metrics_ingestion_zootech %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls ingestion")+
  facet_wrap(~variable, scale="free")

metrics_ingestion_zootech %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_ingestion_zootech %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$CONMOY)-min(df_SC_V3$CONMOY)), 
            pourc_mean = (mean(value)*100)/mean(df_SC_V3$CONMOY))
```

##### b) loadings

```{r loadings ZI, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_ingestion_zootech,id.vars=c("rep", "comp"))

long_loadings %>%
  filter(comp == "comp1")%>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  labs(y= "Loadings", color = "Variables" )+
  ggtitle("Loadings pour composante 1")

long_loadings %>%
  filter(comp == "comp2")%>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  labs(y= "Loadings", color = "Variables" )+
  ggtitle("Loadings pour composante 2")

long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(mean = mean(value))%>%
  filter(mean != 0) %>%
  arrange(desc(mean))

#mean loadings
long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))
```

#### 2. Buckets


##### a) metrics
```{r metriques BI, message=FALSE, warning=FALSE}
metrics_ingestion_buckets %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls ingestion")+
  facet_wrap(~variable, scale="free")

metrics_ingestion_buckets %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_ingestion_buckets %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$CONMOY)-min(df_SC_V3$CONMOY)), 
            pourc_mean = (mean(value)*100)/mean(df_SC_V3$CONMOY))
```

##### b) loadings

```{r loadings BI, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_ingestion_buckets,id.vars=c("rep", "comp"))

#mean loadings
best_loadings = long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))
best_loadings

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))

ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
  annotate(geom = "point", x=metabolites$ppm, y=0, color = "blue", size = 0.5)+
  annotate(geom="text", x=best_flo_pics, y=-0.005, color = "red", label=best_flo_names, size=2)+
  annotate(geom = "point", x=best_flo_pics, y=0, color = "red", size = 0.6))
```

##### c) Corresponding pics  [ERRORS]

```{r add_buckets2metabo, message=FALSE, warning=FALSE}
metabolites = metabolites %>%
  add_column(variable = rep(NA,nrow(metabolites)))

b = as.numeric(names(df_SC_V3[37:length(df_SC_V3)]))
b = as.data.frame(b)

for (x in 1:nrow(metabolites)) {

  bucket = b %>%
    filter(b <= metabolites$ppm[x] & (b > (metabolites$ppm[x]-0.01)))
  metabolites$variable[x] = bucket
}
```

```{r eval=FALSE, include=FALSE}
ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
  annotate(geom = "point", x=metabolites$ppm, y=0, color = "red", size = 0.5, name =metabolites$metabolite))#+
  #annotate("text", x = metabolites$ppm, y = -0.005, label = metabolites$metabolite, color = "red", size = 2)


#bhydroxy
  geom_vline(xintercept = 1.27, color="red", linetype="dashed")+
  geom_vline(xintercept = 2.37, color="red", linetype="dashed")+
  #acetic acid
  geom_vline(xintercept = 2.37, color="red", linetype="dashed")+

metabolites %>%
  filter(ppm >= 1.895 & ppm < 1.975)

metabolites %>%
  filter(metabolite == "B-HydroxyisovalericAcid")


as.numeric(as.character(best_loadings$variable))
```

##### d) ncomp, nvar

nombre composantes
```{r}
loadings_ingestion_buckets %>%
  group_by(rep) %>%
  count()%>%
  ungroup()%>%
  summarise(mean = mean(n))

loadings_ingestion_buckets %>%
  group_by(rep) %>%
  count()%>%
  ggplot(aes(x=as_factor(n)))+
  geom_bar()
```

nombre variables selectionnees : la grille ne fonctionne que pour la composante 1 !
```{r}
long_loadings %>%
  filter(value != 0 & comp == "comp1") %>%
  group_by(rep, comp) %>%
  count()%>%
  ggplot(aes(as_factor(n)))+
  geom_bar()

long_loadings %>%
  filter(value != 0 & comp == "comp2") %>%
  group_by(rep, comp) %>%
  count()%>%
  ggplot(aes(as_factor(n)))+
  geom_bar()
```

#### 3. M+Z+F

##### a) metrics
```{r metriques AI, message=FALSE, warning=FALSE}
metrics_ingestion_all %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls ingestion")+
  facet_wrap(~variable, scale="free")

metrics_ingestion_all %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_ingestion_all %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$CONMOY)-min(df_SC_V3$CONMOY)), 
            pourc_mean = (mean(value)*100)/mean(df_SC_V3$CONMOY))
```

##### b) loadings

```{r loadings AI, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_ingestion_all,id.vars=c("rep", "comp"))

#mean loadings
best_loadings = long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))
best_loadings

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))

ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
  annotate(geom = "point", x=metabolites$ppm, y=0, color = "red", size = 0.5, name =metabolites$metabolite))
```
##### c) ncomp, nvar

nombre composantes
```{r}
loadings_ingestion_all %>%
  group_by(rep) %>%
  count()%>%
  ungroup()%>%
  summarise(mean = mean(n))

loadings_ingestion_all %>%
  group_by(rep) %>%
  count()%>%
  ggplot(aes(x=as_factor(n)))+
  geom_bar()
```

nombre variables selectionnees : la grille ne fonctionne que pour la composante 1 !
```{r}
long_loadings %>%
  filter(value != 0 & comp == "comp1") %>%
  group_by(rep, comp) %>%
  count()%>%
  ggplot(aes(as_factor(n)))+
  geom_bar()

long_loadings %>%
  filter(value != 0 & comp == "comp2") %>%
  group_by(rep, comp) %>%
  count()%>%
  ggplot(aes(as_factor(n)))+
  geom_bar()
```

#### 4. Comparaison {.tabset}

```{r}
cross.val.results = list(
  accuracy = list(
    Z = list(
      corr_spearman = metrics_ingestion_zootech %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_ingestion_zootech %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_ingestion_zootech %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_ingestion_zootech %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_ingestion_zootech %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_ingestion_zootech %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    ),
    M =list(
      corr_spearman = metrics_ingestion_buckets %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_ingestion_buckets %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_ingestion_buckets %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_ingestion_buckets %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_ingestion_buckets %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_ingestion_buckets %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    ),
    All =list(
      corr_spearman = metrics_ingestion_all %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_ingestion_all %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_ingestion_all %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_ingestion_all %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_ingestion_all %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_ingestion_all %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    )
    
  ),
  n_training_instances = nech_sum[[1]],
  n_testing_instances = nech_sum[[2]],
  number.of.rep = 50,
  number.of.folds = 5
)
```

```{r}
comp = algo.test(cross.val.results)
```

##### a) R2
```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("ingestion",3), 
           Predictors = comp$summary$algo[13:15],
           R2 = data.frame(R2 = c(mean(cross.val.results$accuracy$Z$R2),mean(cross.val.results$accuracy$M$R2),mean(cross.val.results$accuracy$All$R2))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)
```

```{r Plot comp ingestion, message=FALSE, warning=FALSE}
p_ingestion <-ggplot(table, aes(x=outcome, y=R2, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#9dc544", "#00a3a6","#423089"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=R2, ymax=R2+sign(R2)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = R2 + sign(R2)*sd +sign(R2)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("R2")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_ingestion
```

##### b) MAE
```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("ingestion",3), 
           Predictors = comp$summary$algo[13:15],
           MAE = data.frame(MAE = c(mean(cross.val.results$accuracy$Z$MAE),mean(cross.val.results$accuracy$M$MAE),mean(cross.val.results$accuracy$All$MAE))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)
```

```{r}
p_ingestion_MAE <-ggplot(table, aes(x=outcome, y=MAE, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#E8A0BF", "#C689C6","#937DC2"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=MAE, ymax=MAE+sign(MAE)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = MAE + sign(MAE)*sd +sign(MAE)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("MAE")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_ingestion_MAE
```

##### c) corr_spearman
```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("ingestion",3), 
           Predictors = comp$summary$algo[13:15],
           corr_spearman = data.frame(corr_spearman = c(mean(cross.val.results$accuracy$Z$corr_spearman),mean(cross.val.results$accuracy$M$corr_spearman),mean(cross.val.results$accuracy$All$corr_spearman))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)
```

```{r}
p_ingestion_sp <-ggplot(table, aes(x=outcome, y=corr_spearman, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#F9D5A7", "#FFB085","#FFA400"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=corr_spearman, ymax=corr_spearman+sign(corr_spearman)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = corr_spearman + sign(corr_spearman)*sd +sign(corr_spearman)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("corr_spearman")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_ingestion_sp
```

##### d) Boxplots R2
```{r}
R2_ingestion = metrics_ingestion_zootech %>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_ingestion_buckets%>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_ingestion_all%>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
R2_ingestion = R2_ingestion %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_increasing_all = all >= zootech) %>%
  dplyr::mutate(is_increasing_bucket = buckets >= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

R2_ingestion %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_bucket == F, "light blue", "light red")), show.legend = F)

R2_ingestion %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_all == F, "light blue", "light red")), show.legend = F)

R2_ingestion %>%
  filter(pred == "all")%>%
  group_by(is_increasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

R2_ingestion %>%
  filter(pred == "buckets")%>%
  group_by(is_increasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


``` 


##### e) Boxplots MAE

```{r}
MAE_ingestion = metrics_ingestion_zootech %>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_ingestion_buckets%>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_ingestion_all%>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
MAE_ingestion = MAE_ingestion %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_decreasing_all = all <= zootech) %>%
  dplyr::mutate(is_decreasing_bucket = buckets <= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

MAE_ingestion %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_decreasing_bucket == F, "light blue", "light red")), show.legend = F)

MAE_ingestion %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_decreasing_all == F, "light blue", "light red")), show.legend = F)

MAE_ingestion %>%
  filter(pred == "all")%>%
  group_by(is_decreasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

MAE_ingestion %>%
  filter(pred == "buckets")%>%
  group_by(is_decreasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


```

##### f) Boxplots spearman
```{r}
corr_spearman_ingestion = metrics_ingestion_zootech %>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_ingestion_buckets%>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_ingestion_all%>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
corr_spearman_ingestion = corr_spearman_ingestion %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_increasing_all = all >= zootech) %>%
  dplyr::mutate(is_increasing_bucket = buckets >= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

corr_spearman_ingestion %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_bucket == F, "light blue", "light red")), show.legend = F)

corr_spearman_ingestion %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_all == F, "light blue", "light red")), show.legend = F)

corr_spearman_ingestion %>%
  filter(pred == "all")%>%
  group_by(is_increasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

corr_spearman_ingestion %>%
  filter(pred == "buckets")%>%
  group_by(is_increasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


``` 

***

### II. Prediction du FCR {.tabset}

```{r data FCR, message=FALSE, warning=FALSE}
#Zootechnie
loadings_fcr_zootech = read_tsv("for_cluster/output_V3/model250/fcr/loadings_fcr_zootech_SC_V3.tsv")
metrics_fcr_zootech =read_tsv("for_cluster/output_V3/model250/fcr/metrics_fcr_zootech_SC_V3.tsv")
  
#Buckets
loadings_fcr_buckets = read_tsv("for_cluster/output_V3/model250/fcr/loadings_fcr_buckets_SC_V3.tsv")
metrics_fcr_buckets = read_tsv("for_cluster/output_V3/model250/fcr/metrics_fcr_buckets_SC_V3.tsv")

#All
loadings_fcr_all = read_tsv("for_cluster/output_V3/model250/fcr/loadings_fcr_all_SC_V3.tsv")
metrics_fcr_all = read_tsv("for_cluster/output_V3/model250/fcr/metrics_fcr_all_SC_V3.tsv")
```

***

#### 1. Zootechnie + Fixes

##### a) metrics
```{r metriques ZF, message=FALSE, warning=FALSE}
metrics_fcr_zootech %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls fcr")+
  facet_wrap(~variable, scale="free")

metrics_fcr_zootech %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_fcr_zootech %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$FCR)-min(df_SC_V3$FCR)), 
            pourc_mean = (mean(value)*100)/mean(df_SC_V3$FCR))
```

##### b) loadings

```{r loadings ZF, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_fcr_zootech,id.vars=c("rep", "comp"))

long_loadings %>%
  filter(comp == "comp1")%>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  labs(y= "Loadings", color = "Variables" )+
  ggtitle("Loadings pour composante 1")

long_loadings %>%
  filter(comp == "comp2")%>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  labs(y= "Loadings", color = "Variables" )+
  ggtitle("Loadings pour composante 2")

long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(mean = mean(value))%>%
  filter(mean != 0) %>%
  arrange(desc(mean))

#mean loadings
long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))
```

#### 2. Buckets


##### a) metrics
```{r metriques BF, message=FALSE, warning=FALSE}
metrics_fcr_buckets %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls fcr")+
  facet_wrap(~variable, scale="free")

metrics_fcr_buckets %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_fcr_buckets %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$FCR)-min(df_SC_V3$FCR)), 
            pourc_mean = (mean(value)*100)/mean(df_SC_V3$FCR))
```

##### b) loadings

```{r loadings BF, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_fcr_buckets,id.vars=c("rep", "comp"))

#mean loadings
best_loadings = long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))
best_loadings

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))

ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
  annotate(geom = "point", x=metabolites$ppm, y=0, color = "blue", size = 0.5)+
  annotate(geom="text", x=best_flo_pics, y=-0.005, color = "red", label=best_flo_names, size=2)+
  annotate(geom = "point", x=best_flo_pics, y=0, color = "red", size = 0.6))
```
##### c) Corresponding pics  [ERRORS]

```{r eval=FALSE, include=FALSE}
best_loadings %>%
  filter(variable %>% metabolites$variable)

metabolites %>%
  filter(ppm >= 1.275 & ppm < 1.285)

metabolites %>%
  filter(metabolite == "B-HydroxyisovalericAcid")
```


#### 3. M+Z+F

##### a) metrics
```{r metriques AF, message=FALSE, warning=FALSE}
metrics_fcr_all %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls fcr")+
  facet_wrap(~variable, scale="free")

metrics_fcr_all %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_fcr_all %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$FCR)-min(df_SC_V3$FCR)), 
            pourc_mean = (mean(value)*100)/mean(df_SC_V3$FCR))
```

##### b) loadings

```{r loadings AF, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_fcr_all,id.vars=c("rep", "comp"))

#mean loadings
best_loadings = long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))
best_loadings

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))

ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
  annotate(geom = "point", x=metabolites$ppm, y=0, color = "red", size = 0.5, name =metabolites$metabolite))
```

***

#### 4. Comparaison {.tabset}

```{r}
cross.val.results = list(
  accuracy = list(
    Z = list(
      corr_spearman = metrics_fcr_zootech %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_fcr_zootech %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_fcr_zootech %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_fcr_zootech %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_fcr_zootech %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_fcr_zootech %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    ),
    M =list(
      corr_spearman = metrics_fcr_buckets %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_fcr_buckets %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_fcr_buckets %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_fcr_buckets %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_fcr_buckets %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_fcr_buckets %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    ),
    All =list(
      corr_spearman = metrics_fcr_all %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_fcr_all %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_fcr_all %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_fcr_all %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_fcr_all %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_fcr_all %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    )
    
  ),
  n_training_instances = nech_sum[[1]],
  n_testing_instances = nech_sum[[2]],
  number.of.rep = 50,
  number.of.folds = 5
)
```

```{r}
comp = algo.test(cross.val.results)
```

##### a) R2

```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("fcr",3), 
           Predictors = comp$summary$algo[13:15],
           R2 = data.frame(R2 = c(mean(cross.val.results$accuracy$Z$R2),mean(cross.val.results$accuracy$M$R2),mean(cross.val.results$accuracy$All$R2))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)

```

```{r Plot comp fcr}
p_fcr <-ggplot(table, aes(x=outcome, y=R2, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#9dc544", "#00a3a6","#423089"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=R2, ymax=R2+sign(R2)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = R2 + sign(R2)*sd +sign(R2)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("R2")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_fcr
```

##### b) MAE
```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("fcr",3), 
           Predictors = comp$summary$algo[13:15],
           MAE = data.frame(MAE = c(mean(cross.val.results$accuracy$Z$MAE),mean(cross.val.results$accuracy$M$MAE),mean(cross.val.results$accuracy$All$MAE))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)
```

```{r}
p_fcr_MAE <-ggplot(table, aes(x=outcome, y=MAE, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#E8A0BF", "#C689C6","#937DC2"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=MAE, ymax=MAE+sign(MAE)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = MAE + sign(MAE)*sd +sign(MAE)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("MAE")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_fcr_MAE
```

##### c) corr_spearman
```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("fcr",3), 
           Predictors = comp$summary$algo[13:15],
           corr_spearman = data.frame(corr_spearman = c(mean(cross.val.results$accuracy$Z$corr_spearman),mean(cross.val.results$accuracy$M$corr_spearman),mean(cross.val.results$accuracy$All$corr_spearman))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)
```

```{r}
p_fcr_sp <-ggplot(table, aes(x=outcome, y=corr_spearman, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#F9D5A7", "#FFB085","#FFA400"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=corr_spearman, ymax=corr_spearman+sign(corr_spearman)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = corr_spearman + sign(corr_spearman)*sd +sign(corr_spearman)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("corr_spearman")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_fcr_sp
```

##### d) Boxplots R2
```{r}
R2_fcr = metrics_fcr_zootech %>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_fcr_buckets%>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_fcr_all%>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
R2_fcr = R2_fcr %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_increasing_all = all >= zootech) %>%
  dplyr::mutate(is_increasing_bucket = buckets >= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

R2_fcr %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_bucket == F, "light blue", "light red")), show.legend = F)

R2_fcr %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_all == F, "light blue", "light red")), show.legend = F)

R2_fcr %>%
  filter(pred == "all")%>%
  group_by(is_increasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

R2_fcr %>%
  filter(pred == "buckets")%>%
  group_by(is_increasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


``` 


##### e) Boxplots MAE

```{r}
MAE_fcr = metrics_fcr_zootech %>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_fcr_buckets%>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_fcr_all%>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
MAE_fcr = MAE_fcr %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_decreasing_all = all <= zootech) %>%
  dplyr::mutate(is_decreasing_bucket = buckets <= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

MAE_fcr %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_decreasing_bucket == F, "light blue", "light red")), show.legend = F)

MAE_fcr %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_decreasing_all == F, "light blue", "light red")), show.legend = F)

MAE_fcr %>%
  filter(pred == "all")%>%
  group_by(is_decreasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

MAE_fcr %>%
  filter(pred == "buckets")%>%
  group_by(is_decreasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


```

##### f) Boxplots spearman
```{r}
corr_spearman_fcr = metrics_fcr_zootech %>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_fcr_buckets%>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_fcr_all%>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
corr_spearman_fcr = corr_spearman_fcr %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_increasing_all = all >= zootech) %>%
  dplyr::mutate(is_increasing_bucket = buckets >= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

corr_spearman_fcr %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_bucket == F, "light blue", "light red")), show.legend = F)

corr_spearman_fcr %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_all == F, "light blue", "light red")), show.legend = F)

corr_spearman_fcr %>%
  filter(pred == "all")%>%
  group_by(is_increasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

corr_spearman_fcr %>%
  filter(pred == "buckets")%>%
  group_by(is_increasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


``` 

***

### III. Prediction de la RFI {.tabset}

```{r data RFI, message=FALSE, warning=FALSE}
#Zootechnie
loadings_rfi_zootech = read_tsv("for_cluster/output_V3/model250/rfi/loadings_rfi_zootech_SC_V3.tsv")
metrics_rfi_zootech =read_tsv("for_cluster/output_V3/model250/rfi/metrics_rfi_zootech_SC_V3.tsv")
  
#Buckets
loadings_rfi_buckets = read_tsv("for_cluster/output_V3/model250/rfi/loadings_rfi_buckets_SC_V3.tsv")
metrics_rfi_buckets = read_tsv("for_cluster/output_V3/model250/rfi/metrics_rfi_buckets_SC_V3.tsv")

#All
loadings_rfi_all = read_tsv("for_cluster/output_V3/model250/rfi/loadings_rfi_all_SC_V3.tsv")
metrics_rfi_all = read_tsv("for_cluster/output_V3/model250/rfi/metrics_rfi_all_SC_V3.tsv")
```

***

#### 1. Zootechnie + Fixes

##### a) metrics
```{r metriques ZR, message=FALSE, warning=FALSE}
metrics_rfi_zootech %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls rfi")+
  facet_wrap(~variable, scale="free")

metrics_rfi_zootech %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_rfi_zootech %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$newRFI)-min(df_SC_V3$newRFI)))
```

##### b) loadings

```{r loadings ZR, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_rfi_zootech,id.vars=c("rep", "comp"))

long_loadings %>%
  filter(comp == "comp1")%>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  labs(y= "Loadings", color = "Variables" )+
  ggtitle("Loadings pour composante 1")

long_loadings %>%
  filter(comp == "comp2")%>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  labs(y= "Loadings", color = "Variables" )+
  ggtitle("Loadings pour composante 2")

long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(mean = mean(value))%>%
  filter(mean != 0) %>%
  arrange(desc(mean))

#mean loadings
long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))
```

#### 2. Buckets


##### a) metrics
```{r metriques BR, message=FALSE, warning=FALSE}
metrics_rfi_buckets %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls rfi")+
  facet_wrap(~variable, scale="free")

metrics_rfi_buckets %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_rfi_buckets %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$newRFI)-min(df_SC_V3$newRFI)))
```

##### b) loadings

```{r loadings BR, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_rfi_buckets,id.vars=c("rep", "comp"))

#mean loadings
best_loadings = long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))
best_loadings

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))

ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
  annotate(geom = "point", x=metabolites$ppm, y=0, color = "blue", size = 0.5)+
  annotate(geom="text", x=best_flo_pics, y=-0.005, color = "red", label=best_flo_names, size=2)+
  annotate(geom = "point", x=best_flo_pics, y=0, color = "red", size = 0.6))
```
##### c) Corresponding pics  [ERRORS]

```{r eval=FALSE, include=FALSE}
best_loadings %>%
  filter(variable %>% metabolites$variable)

metabolites %>%
  filter(ppm >= 1.275 & ppm < 1.285)

metabolites %>%
  filter(metabolite == "B-HydroxyisovalericAcid")
```


#### 3. M+Z+F

##### a) metrics
```{r metriques AR, message=FALSE, warning=FALSE}
metrics_rfi_all %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls rfi")+
  facet_wrap(~variable, scale="free")

metrics_rfi_all %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))

metrics_rfi_all %>%
  filter(variable== "MAE") %>%
  summarise(pourc_range = (mean(value)*100)/(max(df_SC_V3$newRFI)-min(df_SC_V3$newRFI)))
```

##### b) loadings

```{r loadings AR, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_rfi_all,id.vars=c("rep", "comp"))

#mean loadings
best_loadings = long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))
best_loadings

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))

ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
   annotate(geom = "point", x=metabolites$ppm, y=0, color = "blue", size = 0.5)+
  annotate(geom="text", x=best_flo_pics, y=-0.005, color = "red", label=best_flo_names, size=2)+
  annotate(geom = "point", x=best_flo_pics, y=0, color = "red", size = 0.6))
```

#### 4. Comparaison {.tabset}

```{r}
cross.val.results = list(
  accuracy = list(
    Z = list(
      corr_spearman = metrics_rfi_zootech %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_rfi_zootech %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_rfi_zootech %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_rfi_zootech %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_rfi_zootech %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_rfi_zootech %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    ),
    M =list(
      corr_spearman = metrics_rfi_buckets %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_rfi_buckets %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_rfi_buckets %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_rfi_buckets %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_rfi_buckets %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_rfi_buckets %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    ),
    All =list(
      corr_spearman = metrics_rfi_all %>%
        filter(variable == "corr_spearman")%>%
        select(value)%>%
        as_vector(),
      R2 =metrics_rfi_all %>%
        filter(variable == "R2")%>%
        select(value)%>%
        as_vector(),
      MSE =metrics_rfi_all %>%
        filter(variable == "MSE")%>%
        select(value)%>%
        as_vector(),
      RMSE =metrics_rfi_all %>%
        filter(variable == "RMSE")%>%
        select(value)%>%
        as_vector(),
      bias =metrics_rfi_all %>%
        filter(variable == "bias")%>%
        select(value)%>%
        as_vector(),
      MAE =metrics_rfi_all %>%
        filter(variable == "MAE")%>%
        select(value)%>%
        as_vector()
    )
    
  ),
  n_training_instances = nech_sum[[1]],
  n_testing_instances = nech_sum[[2]],
  number.of.rep = 50,
  number.of.folds = 5
)
```

```{r}
comp = algo.test(cross.val.results)
```
##### a) R2

```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("rfi",3), 
           Predictors = comp$summary$algo[13:15],
           R2 = data.frame(R2 = c(mean(cross.val.results$accuracy$Z$R2),mean(cross.val.results$accuracy$M$R2),mean(cross.val.results$accuracy$All$R2))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)

```

```{r Plot comp rfi}
p_rfi <-ggplot(table, aes(x=outcome, y=R2, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#9dc544", "#00a3a6","#423089"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=R2, ymax=R2+sign(R2)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = R2 + sign(R2)*sd +sign(R2)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("R2")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_rfi
```

##### b) MAE
```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("rfi",3), 
           Predictors = comp$summary$algo[13:15],
           MAE = data.frame(MAE = c(mean(cross.val.results$accuracy$Z$MAE),mean(cross.val.results$accuracy$M$MAE),mean(cross.val.results$accuracy$All$MAE))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)
```

```{r}
p_rfi_MAE <-ggplot(table, aes(x=outcome, y=MAE, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#E8A0BF", "#C689C6","#937DC2"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=MAE, ymax=MAE+sign(MAE)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = MAE + sign(MAE)*sd +sign(MAE)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("MAE")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_rfi_MAE
```

##### c) corr_spearman
```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("rfi",3), 
           Predictors = comp$summary$algo[13:15],
           corr_spearman = data.frame(corr_spearman = c(mean(cross.val.results$accuracy$Z$corr_spearman),mean(cross.val.results$accuracy$M$corr_spearman),mean(cross.val.results$accuracy$All$corr_spearman))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[13:15],
           letter = comp$summary$letter[13:15])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)
```

```{r}
p_rfi_sp <-ggplot(table, aes(x=outcome, y=corr_spearman, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#F9D5A7", "#FFB085","#FFA400"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=corr_spearman, ymax=corr_spearman+sign(corr_spearman)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = corr_spearman + sign(corr_spearman)*sd +sign(corr_spearman)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("corr_spearman")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_rfi_sp
```

##### d) Boxplots R2
```{r}
R2_rfi = metrics_rfi_zootech %>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_rfi_buckets%>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_rfi_all%>%
  filter(variable == "R2") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
R2_rfi = R2_rfi %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_increasing_all = all >= zootech) %>%
  dplyr::mutate(is_increasing_bucket = buckets >= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

R2_rfi %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_bucket == F, "light blue", "light red")), show.legend = F)

R2_rfi %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_all == F, "light blue", "light red")), show.legend = F)

R2_rfi %>%
  filter(pred == "all")%>%
  group_by(is_increasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

R2_rfi %>%
  filter(pred == "buckets")%>%
  group_by(is_increasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


``` 


##### e) Boxplots MAE

```{r}
MAE_rfi = metrics_rfi_zootech %>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_rfi_buckets%>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_rfi_all%>%
  filter(variable == "MAE") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
MAE_rfi = MAE_rfi %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_decreasing_all = all <= zootech) %>%
  dplyr::mutate(is_decreasing_bucket = buckets <= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

MAE_rfi %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_decreasing_bucket == F, "light blue", "light red")), show.legend = F)

MAE_rfi %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_decreasing_all == F, "light blue", "light red")), show.legend = F)

MAE_rfi %>%
  filter(pred == "all")%>%
  group_by(is_decreasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

MAE_rfi %>%
  filter(pred == "buckets")%>%
  group_by(is_decreasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


```

##### f) Boxplots spearman
```{r}
corr_spearman_rfi = metrics_rfi_zootech %>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_rfi_buckets%>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_rfi_all%>%
  filter(variable == "corr_spearman") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
corr_spearman_rfi = corr_spearman_rfi %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_increasing_all = all >= zootech) %>%
  dplyr::mutate(is_increasing_bucket = buckets >= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

corr_spearman_rfi %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_bucket == F, "light blue", "light red")), show.legend = F)

corr_spearman_rfi %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_increasing_all == F, "light blue", "light red")), show.legend = F)

corr_spearman_rfi %>%
  filter(pred == "all")%>%
  group_by(is_increasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

corr_spearman_rfi %>%
  filter(pred == "buckets")%>%
  group_by(is_increasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


``` 

***

### IV. Prediction de la lignee {.tabset}
```{r data lignee, message=FALSE, warning=FALSE}
#Zootechnie
loadings_lignee_zootech = read_tsv("for_cluster/output_V3/model250/lignee/loadings_lignee_zootech_SC_V3.tsv")
metrics_lignee_zootech =read_tsv("for_cluster/output_V3/model250/lignee/metrics_lignee_zootech_SC_V3.tsv")
  
#Buckets
loadings_lignee_buckets = read_tsv("for_cluster/output_V3/model250/lignee/loadings_lignee_buckets_SC_V3.tsv")
metrics_lignee_buckets = read_tsv("for_cluster/output_V3/model250/lignee/metrics_lignee_buckets_SC_V3.tsv")

#All
loadings_lignee_all = read_tsv("for_cluster/output_V3/model250/lignee/loadings_lignee_all_SC_V3.tsv")
metrics_lignee_all = read_tsv("for_cluster/output_V3/model250/lignee/metrics_lignee_all_SC_V3.tsv")
```

***

#### 1. Zootechnie + Fixes

##### a) metrics
```{r metriques ZL, message=FALSE, warning=FALSE}
metrics_lignee_zootech %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls lignee")+
  facet_wrap(~variable, scale="free")

metrics_lignee_zootech %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))
```

##### b) loadings

```{r loadings ZL, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_lignee_zootech,id.vars=c("rep", "comp"))

long_loadings %>%
  filter(comp == "comp1")%>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  labs(y= "Loadings", color = "Variables" )+
  ggtitle("Loadings pour composante 1")

long_loadings %>%
  filter(comp == "comp2")%>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  labs(y= "Loadings", color = "Variables" )+
  ggtitle("Loadings pour composante 2")

long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(mean = mean(value))%>%
  filter(mean != 0) %>%
  arrange(desc(mean))

#mean loadings
long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))
```

#### 2. Buckets


##### a) metrics
```{r metriques BL, message=FALSE, warning=FALSE}
metrics_lignee_buckets %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour splsda lignee")+
  facet_wrap(~variable, scale="free")

metrics_lignee_buckets %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))
```

##### b) loadings

```{r loadings BL, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_lignee_buckets,id.vars=c("rep", "comp"))

#mean loadings
best_loadings = long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))
best_loadings

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))

ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
  annotate(geom = "point", x=metabolites$ppm, y=0, color = "blue", size = 0.5)+
  annotate(geom="text", x=best_flo_pics, y=-0.005, color = "red", label=best_flo_names, size=2)+
  annotate(geom = "point", x=best_flo_pics, y=0, color = "red", size = 0.6))
```
##### c) ncomp, nvar

nombre composantes
```{r}
loadings_lignee_buckets %>%
  group_by(rep) %>%
  count()%>%
  ungroup()%>%
  summarise(mean = mean(n))

loadings_lignee_buckets  %>%
  group_by(rep) %>%
  count()%>%
  ggplot(aes(x=as_factor(n)))+
  geom_bar()
```

nombre variables selectionnees : la grille ne fonctionne que pour la composante 1 !
```{r}
long_loadings %>%
  filter(value != 0 & comp == "comp1") %>%
  group_by(rep, comp) %>%
  count()%>%
  ggplot(aes(as_factor(n)))+
  geom_bar()

long_loadings %>%
  filter(value != 0 & comp == "comp2") %>%
  group_by(rep, comp) %>%
  count()%>%
  ggplot(aes(as_factor(n)))+
  geom_bar()
```

##### c) Corresponding pics  [ERRORS]

```{r eval=FALSE, include=FALSE}
best_loadings %>%
  filter(variable %>% metabolites$variable)

metabolites %>%
  filter(ppm >= 6.935 & ppm < 6.955)

metabolites %>%
  filter(metabolite == "B-HydroxyisovalericAcid")
```


#### 3. M+Z+F

##### a) metrics
```{r metriques AL, message=FALSE, warning=FALSE}
metrics_lignee_all %>%
  ggplot(aes(variable, value)) +
  geom_jitter(color = "light grey", size=1.5, alpha=0.30) +
  geom_boxplot(aes(color=variable))+
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="black", fill="black") +
  labs(y= "Metriques", color = "Mesures" )+
  ggtitle("Mesures pour spls lignee")+
  facet_wrap(~variable, scale="free")

metrics_lignee_all %>%
  group_by(variable) %>%
  summarise(min = min(value), mean = mean(value), max = max(value))
```

##### b) loadings

```{r loadings AL, message=FALSE, warning=FALSE}
long_loadings = reshape2::melt(loadings_lignee_all,id.vars=c("rep", "comp"))

#mean loadings
best_loadings = long_loadings %>%
  filter (comp == "comp1") %>%
  group_by(comp, variable) %>%
  summarise(min= min(value), mean = mean(value), max = max(value), mean_abs = mean(abs(value)))%>%
  filter(mean != 0) %>%
  arrange(desc(mean_abs))
best_loadings

#count loadings
long_loadings %>%
  filter (comp == "comp1" & value != 0) %>%
  group_by(comp, variable) %>%
  count() %>%
  arrange(desc(n))

ggplotly(
  best_loadings %>%
  ggplot(aes(x=as.numeric(as.character(best_loadings$variable)), y=mean_abs))+
  geom_col()+
   annotate(geom = "point", x=metabolites$ppm, y=0, color = "blue", size = 0.5)+
  annotate(geom="text", x=best_flo_pics, y=-0.005, color = "red", label=best_flo_names, size=2)+
  annotate(geom = "point", x=best_flo_pics, y=0, color = "red", size = 0.6))
```
##### c) ncomp, nvar

nombre composantes
```{r}
loadings_lignee_all %>%
  group_by(rep) %>%
  count()%>%
  ungroup()%>%
  summarise(mean = mean(n))

loadings_lignee_all %>%
  group_by(rep) %>%
  count()%>%
  ggplot(aes(x=as_factor(n)))+
  geom_bar()
```

nombre variables selectionnees : la grille ne fonctionne que pour la composante 1 !
```{r}
long_loadings %>%
  filter(value != 0 & comp == "comp1") %>%
  group_by(rep, comp) %>%
  count()%>%
  ggplot(aes(as_factor(n)))+
  geom_bar()

long_loadings %>%
  filter(value != 0 & comp == "comp2") %>%
  group_by(rep, comp) %>%
  count()%>%
  ggplot(aes(as_factor(n)))+
  geom_bar()
```

#### 4. Comparaison

##### a) Comparaisons metrics

```{r}
cross.val.results = list(
  accuracy = list(
    Z = list(
      BER = metrics_lignee_zootech %>%
        filter(variable == "BER")%>%
        select(value)%>%
        as_vector()
    ),
    M =list(
      BER = metrics_lignee_buckets %>%
        filter(variable == "BER")%>%
        select(value)%>%
        as_vector()
    ),
    All =list(
      BER = metrics_lignee_all %>%
        filter(variable == "BER")%>%
        select(value)%>%
        as_vector()
    )
    
  ),
  n_training_instances = nech_sum[[1]],
  n_testing_instances = nech_sum[[2]],
  number.of.rep = 50,
  number.of.folds = 5
)
```

```{r}
comp = algo.test(cross.val.results)
```

```{r}
table = data.frame(diet_seq = rep("DAC",3),
           outcome = rep("lignee",3), 
           Predictors = comp$summary$algo[1:3],
           BER = data.frame(BER = c(mean(cross.val.results$accuracy$Z$BER),mean(cross.val.results$accuracy$M$BER),mean(cross.val.results$accuracy$All$BER))),
           sd = gsub('[()]', '',comp$summary$`(sd)`)[1:3],
           letter = comp$summary$letter[1:3])

table$letter = as_factor(table$letter)
table$sd = as.numeric(table$sd)

```

```{r Plot comp lignee}
p_lignee <-ggplot(table, aes(x=outcome, y=BER, fill=Predictors)) +
  #barplot
  geom_col(width = 0.5,#bar width
           position = position_dodge(0.6),#space between bars on the same x
           colour="black", size=0.2)+#colour and size of bar lines
  scale_fill_manual(values=c("#9dc544", "#00a3a6","#423089"),#colors of bars
                    name="Predictor set:")+#name for the legend
  #error bars
  geom_errorbar(aes(ymin=BER, ymax=BER+sign(BER)*sd),#length of error bars
                 width=0.2,#width of error bars
                 position=position_dodge(0.6),#space between bars on the same x
                stat="identity")+
  #letters to indicate significant differences or non significant
  geom_text(aes(label = letter,#name of the variable used for labelling
                y = BER + sign(BER)*sd +sign(BER)*0.05),#vertical position of the letter
            position = position_dodge(0.6),#space between bars on the same x
            family="Raleway", size=4.5)+#letter label style
  #theme
  theme_classic()+
  #legend
  theme(legend.position="top")+#legend position
  theme(legend.title = element_text(colour="black", size=11, family="Raleway"))+#legend title style
  theme(legend.text = element_text(colour="black", size=10, family="sans"))+#legend text style
  #grid style
  theme(panel.grid.major.y = element_line(color = "grey80", size = 0.5, linetype = 1))+#horizontal grid style
  #x axis
  xlab("Predicted outcome")+#x axis title
  theme(axis.title.x = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=-0.8))+# x axis title style
  theme(axis.text.x = element_text(colour="grey30", size=10, family="sans"))+# x axis text style
  #y axis
  ylab("BER")+#y axis title
  theme(axis.title.y = element_text(colour="black", size=10, family="Raleway SemiBold", vjust=+2))+# y axis title style
  theme(axis.text.y = element_text(colour="grey30", size=10, family="sans"))

p_lignee
```

##### b) Comparaisons boxplots 
```{r}
BER_lignee = metrics_lignee_zootech %>%
  filter(variable == "BER") %>%
  add_column("pred" = rep("zootech", 250)) %>%
  rbind(
metrics_lignee_buckets%>%
  filter(variable == "BER") %>%
  add_column("pred" = rep("buckets", 250))
) %>%
  rbind(
metrics_lignee_all%>%
  filter(variable == "BER") %>%
  add_column("pred" = rep("all", 250))
)
```

```{r}
BER_lignee = BER_lignee %>%
    tidyr::spread(pred, value) %>%
    dplyr::mutate(is_decreasing_all = all <= zootech) %>%
  dplyr::mutate(is_decreasing_bucket = buckets <= zootech)%>%
    tidyr::gather("pred", "value", 3:5)

BER_lignee %>%
  filter(pred != "all")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_decreasing_bucket == F, "light blue", "light red")), show.legend = F)

BER_lignee %>%
  filter(pred != "buckets")%>%
  ggplot(aes(x= pred, y=value))+
  geom_boxplot()+
  geom_point(aes(group=id),color = "black", size=1.5, alpha=0.30)+
  geom_line(aes(group=id, color = if_else(is_decreasing_all == F, "light blue", "light red")), show.legend = F)

BER_lignee %>%
  filter(pred == "all")%>%
  group_by(is_decreasing_all) %>%
  count()%>%
  mutate (pour = (n*100)/250)

BER_lignee %>%
  group_by(is_decreasing_bucket) %>%
  count() %>%
  mutate (pour = (n*100)/250)


```

***

## Comparaisons {.tabset}


### 1. R2
```{r message=FALSE, warning=FALSE}
library(cowplot)
plot_grid(p_ingestion+
            scale_y_continuous(
              breaks = seq(0, 0.8,0.2), 
              limits = c(0,1)),
          p_fcr+
            scale_y_continuous(
              breaks = seq(0, 0.8,0.2), 
              limits = c(0,1)),
          p_rfi+
            scale_y_continuous(
              breaks = seq(0, 0.8,0.2), 
              limits = c(0,1)), 
          ncol = 3, nrow = 1)


```

### 2. corr_spearman

```{r message=FALSE, warning=FALSE}
plot_grid(p_ingestion_sp+
            scale_y_continuous(
              breaks = seq(-0.2, 0.8,0.2), 
              limits = c(0,1)),
          p_fcr_sp+
            scale_y_continuous(
              breaks = seq(-0.2, 0.8,0.2), 
              limits = c(0,1)),
          p_rfi_sp+
            scale_y_continuous(
              breaks = seq(-0.2, 0.8,0.2), 
              limits = c(0,1)), 
          ncol = 3, nrow = 1)


```

## Session Info
```{r}
sessionInfo()
```